%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Frontend Developer} % Job title
    {Whitelogic} % Organization
    {Chennai, India} % Location
    {Winter 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Client Technologies Developer in a startup organization}
        \item {Built a web application from scratch using Angular 2 as the framework.
            Worked with a REST-api along with Typescript to develop the app. The MVC Design 
            Pattern was followed to create scalable code. The application was created up to
            industry standards, and is being deployed in a few major Fortune 500 companies 
            (further details are under NDA).  }
      \end{cvitems}
    }
    
    \cventry
      {Frontend Developer, under Prof. Manindra Agarwal} % Job title
      {New York Office, IIT Kanpur} % Organization
      {Kanpur, India} % Location
      {Summer 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Worked in a team to develop an information management and retrieval system for New York office of IITK.Worked on a scalable Web-Application.}
      \item {Led a team of 4 members and was a peer mentor during the course of the
          internship.}
      \item	{Implemented Reactive Forms with better validation giving better UX to the user.}
      \item {Implemented linking of user Facebook account to our Web-App.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
